{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-04 Paper/main.tex
ggplot replacements for function plots
Comment for new curves

	\subsection{Generating Similar Curves}
	To avoid small sample problems, we generated 200 similar curves from the gasoline dataset, motivated by \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}. First, the initial curves are expressed in terms of a generated B-spline basis which is created using 50 knots. These smooth curves are then centered, before applying the \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}. It is assumed that the scores follow a normal distribution, thus, the new realizations for the scores are drawn from a multivariate normal $\tilde{\xi} = \left(\tilde{\xi}_{1},\: \dots \:, \tilde{\xi}_{J}\right)' \sim \mathcal{N}(0_J, \; diag(\hat{\lambda}_1,\: \dots\:, \hat{\lambda}_J))$. Finally, we obtain the generated curves $NIR_{sim}$

@@

		\vspace{0.1cm}
		\begin{figure}
			\centering
			\begin{minipage}{.5\textwidth}
				\centering
  				\includegraphics[width=\textwidth]{../Graphics/smooth_function.png}
  				\caption{$f_1(t)$, smooth function}
  				\label{fig:test1}
			\end{minipage}%
			\begin{minipage}{.5\textwidth}
	  			\centering
  				\includegraphics[width=\textwidth]{../Graphics/bumpy_function.png}
  				\caption{$f_2(t)$, bumpy function}
  				\label{fig:test2}
			\end{minipage}
		\end{figure}

>>>>

	\subsection{Generating Similar Curves}
	To avoid small sample problems, we generated 200 similar curves from the gasoline dataset, motivated by \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}. First, the initial curves are expressed in terms of a generated B-spline basis which is created using 50 knots. These smooth curves are then centered, before applying the \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}. It is assumed that the scores follow a normal distribution, thus, the new realizations for the scores are drawn from a multivariate normal distribution $\tilde{\xi} = \left(\tilde{\xi}_{1},\: \dots \:, \tilde{\xi}_{J}\right)' \sim \mathcal{N}(0_J, \; diag(\hat{\lambda}_1,\: \dots\:, \hat{\lambda}_J))$. Finally, we obtain the generated curves $NIR_{sim}$

	{\color{blue} This has to be more precise. We don't really use $\hat{\nu}_j(t)$ but $\tilde{\nu}^{m,L}(t)$ for a large $L$.}

@@

		\vspace{0.1cm}
		\begin{figure}
			\centering
			\begin{minipage}{.5\textwidth}
				\centering
  				\includegraphics[width=\textwidth]{../Graphics/f1_plot.pdf}
  				\caption{$f_1(t)$, smooth function}
  				\label{fig:test1}
			\end{minipage}%
			\begin{minipage}{.5\textwidth}
	  			\centering
  				\includegraphics[width=\textwidth]{../Graphics/f2_plot.pdf}
  				\caption{$f_2(t)$, bumpy function}
  				\label{fig:test2}
			\end{minipage}
		\end{figure}
